Why do capacitors usually only have a small value

### 2019-11-23 notes/sideband_obe/sideband_obe.tex
[notes] reorganize

When the trapping frequency is much smaller than the line width, $\Gamma^\alpha_m$ is independent with $m$ and is proportional to the corresponding pumping power. $\Gamma^{\alpha\beta}_{mn}$ can be written as,
\eqar{
  \Gamma^{\alpha\beta}_{mn}=&\Gamma^{\alpha\beta}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma^{aa}&\Gamma^{ab}&\Gamma^{ac}\\
    \Gamma^{ba}&\Gamma^{bb}&\Gamma^{bc}\\
    \Gamma^{ca}&\Gamma^{cb}&\Gamma^{cc}
  \end{pmatrix}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma^aB^{aa}&\Gamma^bB^{ab}&\Gamma^cB^{ac}\\
    \Gamma^aB^{ba}&\Gamma^bB^{bb}&\Gamma^cB^{bc}\\
    \Gamma^aB^{ca}&\Gamma^bB^{cb}&\Gamma^cB^{cc}
  \end{pmatrix}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma_1B^{aa}&\varepsilon\Gamma_2B^{ab}&\Gamma_2B^{ac}\\
    \Gamma_1B^{ba}&\varepsilon\Gamma_2B^{bb}&\Gamma_2B^{bc}\\
    \Gamma_1B^{ca}&\varepsilon\Gamma_2B^{cb}&\Gamma_2B^{cc}
  \end{pmatrix}\gamma_{mn}
}
where $B^{\alpha\beta}$ is the branching ratio, $\Gamma_1$ is the $F$ pumping power ($(1, 1) \rightarrow (2, 2)'$ light), $\Gamma_2$ is the $m_F$ pumping power ($(2, 1) \rightarrow (2, 2)'$ light) and $\varepsilon$ is the off-resonance coupling of the $m_F$ pumping light to the $(2, 2) \rightarrow (2, 3)'$ transition.

>>>>

When the trapping frequency is much smaller than the line width, $\Gamma^\alpha_m$ is independent with $m$ and is proportional to the corresponding pumping power. $\Gamma^{\alpha\beta}_{mn}$ can be written as,
\eqar{
  \Gamma^{\alpha\beta}_{mn}=&\Gamma^{\alpha\beta}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma^{aa}&\Gamma^{ab}&\Gamma^{ac}\\
    \Gamma^{ba}&\Gamma^{bb}&\Gamma^{bc}\\
    \Gamma^{ca}&\Gamma^{cb}&\Gamma^{cc}
  \end{pmatrix}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma^aB^{aa}&\Gamma^bB^{ab}&\Gamma^cB^{ac}\\
    \Gamma^aB^{ba}&\Gamma^bB^{bb}&\Gamma^cB^{bc}\\
    \Gamma^aB^{ca}&\Gamma^bB^{cb}&\Gamma^cB^{cc}
  \end{pmatrix}\gamma_{mn}\\
  =&\begin{pmatrix}
    \Gamma_1B^{aa}&\varepsilon\Gamma_2B^{ab}&\Gamma_2B^{ac}\\
    \Gamma_1B^{ba}&\varepsilon\Gamma_2B^{bb}&\Gamma_2B^{bc}\\
    \Gamma_1B^{ca}&\varepsilon\Gamma_2B^{cb}&\Gamma_2B^{cc}
  \end{pmatrix}\gamma_{mn}
}
where $B^{\alpha\beta}$ is the branching ratio, $\Gamma_1$ is the $F$ pumping power ($(1, 1) \rightarrow (2, 2)'$ light), $\Gamma_2$ is the $m_F$ pumping power ($(2, 1) \rightarrow (2, 2)'$ light), $\varepsilon$ is the off-resonance coupling of the $m_F$ pumping light to the $(2, 2) \rightarrow (2, 3)'$ transition and $\gamma_{mn}$ is the state independent direction averaged recoil coupling between state $m$ and $n$.
\eqar{
  \gamma_{mn}=&\gamma_{nm}\\
  \sum_{m}\gamma_{mn}=&1
}

With $0.6\%$ polarization misalignment and for $\Gamma_1$ and $\Gamma_2$ normalized to the pumping rate of the $(1, 1)$ and $(2, 1)$ states.
\eqar{
  \Gamma^{\alpha\beta}=&\begin{pmatrix}
    0.500\Gamma_1&0.006\Gamma_2&0.500\Gamma_2\\
    0.333\Gamma_1&0.171\Gamma_2&0.333\Gamma_2\\
    0.167\Gamma_1&0.002\Gamma_2&0.167\Gamma_2
  \end{pmatrix}\\
  \Gamma^a_m=&\Gamma_1\\
  \Gamma^b_m=&0.179\Gamma_2\\
  \Gamma^c_m=&\Gamma_2
}
If we use the $D1$ transition to do the pumping instead the matrix becomes
\eqar{
  \Gamma^{\alpha\beta}=&\begin{pmatrix}
    0.500\Gamma_1&0.006\Gamma_2&0.500\Gamma_2\\
    0.333\Gamma_1&0.004\Gamma_2&0.333\Gamma_2\\
    0.167\Gamma_1&0.002\Gamma_2&0.167\Gamma_2
  \end{pmatrix}\\
  \Gamma^a_m=&\Gamma_1\\
  \Gamma^b_m=&0.012\Gamma_2\\
  \Gamma^c_m=&\Gamma_2
}
